Forecasting the 2024 U.S. Presidential Election

### 2024-11-03 paper/paper.qmd
Update paper.

# Model details {#sec-model-details}

>>>>

# Model details {#sec-model-details}
```{r}
data_filtered <- read_csv(here::here("data/02-analysis_data/model_data.csv"))
data_filtered <- data_filtered %>%
  mutate(predicted_pct = predict(penn_model, newdata = ., type = "response"))
summary(penn_model)

ggplot(penn, aes(x = start_date_numeric, y = pct, color = candidate_name)) +
  geom_point(aes(y = pct), alpha = 0.5) + 
  geom_line(aes(y = predicted_pct), size = 1) + 
  labs(title = "Pennsylvania - Predicted vs True",
       x = "Date",
       y = "Rate of support") +
  theme_minimal() +
  scale_y_continuous(labels = scales::percent_format())
